Modal Abstractions for Virtualizing Memory Addresses

### 2023-03-29 programlogic.tex
+

@@

As part of assertions on our machine state ($\sigma$), we abstract memory addresses and registers naming their relevant values through well-known separation logic assertion \textit{points-to}.

>>>>

Based on these perspectives, we coneptualize truth on an address-space as indexed by its roots address, therefore. we lift standard bi proposition to be indexed with $\mathcal{W}_{64}$ as shown in Figure \ref{fig:vprop}. Contesequently. all abstractions we explain in this section as part of our address-space logic are type $\textsf{vProp }\Sigma$.
\textsf{vProp } \Sigma \; : \; \textsf{bi} \; \stackrel{def}{=} \mathcal{W}_{64} -\textsf{b}> \textsf{iPropI } \Sigma
\caption{$\textsf{vProp }\Sigma$: Root-Address Indexed Address-Space Proposition}
  \label{fig:vprop}

@@

We abstract memory addresses and registers naming their relevant values through well-known separation logic assertion \textit{points-to}.
